Draft Report

### 2020-11-16 DraftReport.Rmd
Updated Section 3 of the report.

>>>>

### 3. Limitations of the Model

The most general requirement for the linear model is that data points be independent and identically distributed (IID). While for the most part the events of one state will primarily affect that single state, travel by individuals spreading the virus across state lines is an inevitable occurence. This may cause the spread of a virus within one state to be influenced by those around it, or generally by its position in the country. While this is acknowledged to occur, the effect is likely minor compared to the demographic and policy data collected state by state which would affect the spread of the virus. Therefore it is relatively safe for this assumption to be met.

Secondly, the process being modeled must be described by a linear conditional expectation function of the variables which are included, in order for the linear regression to be valid. This can be assessed after the fact by visualizing the model over the range of each variable alongside the data, or also by visualizing the residuals over the range of each variable.

Related to the relationship of the residuals to the data, homoskedasticity can be assessed by visualizing the size of residuals across the range of each variable. Alternatively, it can also be done via the Breusch-Pagan test to more objectively determine whether homoskedasticity is not present in the data.

Perfect colinearity is automatically detected by the R regression algorithms, which drop potential variables if they have complete colinearity with another variable. Near perfect colinearity is more problematic to detect, but a common hint to its existence is large standard errors on colinear features. Conceptually, the variables which may have an important colinearity in the final model are

Finally, normally distributed errors can be easily assessed by a histogram of the residuals around zero.
